---
title: "Guide"
---

```{r echo=FALSE}
library(tibble)
library(gt)
```



```{r}
#| label: objectives
#| echo: FALSE
#| message: true
#| warning: false
#| paged-print: true
outcome_goals <- tribble(
  ~outcome, ~objective, ~tool,
  "Increased Guided Reading and Writing", "75%", "Session Summary Form",
  "Grade Promotion", "90%", "grade promotion Form",
  "Decrease in Absenteeism", "60%", "Attendance Tracking Form", 
  "Sense of Self", "80%", "Girl Survey",
  "Positive Values", "75%", "Girl Survey",
  "Challenge Seeking", "62%", "Girl Survey",
  "Healthy Relationships", "60%", "Girl Survey",
  "Community Problem Solving", "57%",  "Girl Survey"
) 

outcome_goals %>% 
  gt::gt() %>% 
  #gt::cols_hide(3) %>%
  tab_header(
    title = md("**Get REAL! Objectives**")
  ) %>%
  
  gtExtras::gt_theme_538(quiet = TRUE) -> outcome_goals_tbl

outcome_goals_tbl

```



# Data Entry Guide

## Session Summary
This data measures progress toward the objective **Increased Guided Reading and Writing**. The session summary tracks your activities throughout the year.

**When to enter:** Update regularly throughout the program year to maintain accurate records.

**Best practice:** Enter session data after each meeting or weekly

---

## Girl Survey
This data measures the **Life Skills Objectives**.

Pre and post surveys are essential for measuring participant outcomes in the Get REAL! program.

**When to enter:** 
- **Pre-survey:** At program start or when a girl joins
- **Post-survey:** At program conclusion or when a girl completes the program

*Note: Surveys can be entered at any time, but both pre and post surveys are required for each participant.*

---

## Attendance
This data measures the **Decreased Absenteeism** objective.

**When to enter:**  - **Minimum requirement:** Enter attendance at two data points (e.g., Quarter 1 and Quarter 4, or baseline and endpoint of program participant)

**Best practice:** Enter attendance data regularly

---

## Grade Promotion
Grade promotion status confirms academic progress for program participants.

**When to enter:** At the end of the school year once promotion status is confirmed, or as soon as you receive this information.

---
### Data Entry Reports
Nearly every Saturday, data is pulled from Qualtrics and data entry reports are generated for each data source. An email will be sent with a link to your report.
During the data pull, data quality is assessed and duplicate entries are identified and reported.

### Questions
If you have questions, concerns, or want to review your data, email me at kevingilds@gmail.com and I will send you a CSV file with the requested information.



